Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
first hacky attempts to turn verbatims into tables. looks bad

\begin{itemize}
\item EXPT  using n=1 parse for DPM variants
\label{tab:facorr:subgraphs}
\begin{verbatim}
   metric      r
  --------   -----
  F[dl;lh]   0.226
  BLEU4      0.218  # +1 smoothing
  F[dlh]     0.185
  TER       -0.173
\end{verbatim}

  point: using partial-labeling (dl,lh) much better than full
  link. Also, using Charniak parser as labeler seems to work, LFG not
  necessary

>>>>

  \begin{table}
    % \centering
    \caption{$dl,lh$ decompositions are
      more correlated with the fluency-adequacy average than BLEU$_4$
      or $dlh$ decompositions.}
    \begin{tabular}{lr}
      metric  &    $r$ \\
      \hline
      $F[dl,lh]$ &   0.226 \\
       % # +1 smoothing
      BLEU$_4$ &   0.218 \\
      $F[dlh]$ &     0.185 \\
      TER &      -0.173 \\
    \end{tabular}
    \label{tab:facorr:subgraphs}
\end{table}

Table~\ref{tab:facorr:subgraphs} indicates that: using
partial-labeling (dl,lh) much better than full link. Also, using
Charniak parser as labeler seems to work, LFG not necessary
Here, $n=1$ and only the $F[\cdot]$ score combination is shown.

\begin{itemize}
